---
title: "07A_MI_imputiert"
output: html_document
date: "2023-04-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages

```{r}
library(tidyverse)
library(lavaan)
library(semTools)
library(dplyr)
library(haven)
```

# import data
```{r}
tbi13<-read_sav("Datensatz_3_Masterarbeit_DT_22_23.sav")
load("data_final.Rdata")
```

## preparation of tbi-data
```{r}
# removing unnecessary columns
tbi13<-subset(tbi13) %>% 
  dplyr::select(-ends_with("prae")) %>% 
  dplyr::select(-contains("RAPID")) %>% 
  dplyr::select(-c("Laufende_Nummer", "Zentrum", "TestdatumJ", "TestdatumE", "Schweregrad", "KOSCHI",
                   "BesVer_Mutter", "BesVer_Vater", "stationary", "ambulatory", "direct",
                   "indirect", "multilingual", "Testdatum.Untersucher")) %>% 
  dplyr::select(-contains("SHT")) %>% 
  dplyr::select(-ends_with("tri")) %>% 
  dplyr::select(-starts_with("Low")) %>% 
  dplyr::select(-starts_with("U")) %>%
  dplyr::select(-starts_with("High")) %>%
  dplyr::select(-starts_with("frontal")) %>%
  dplyr::select(-starts_with("temporal")) %>% 
  dplyr::select(-starts_with("parietal")) %>% 
  dplyr::select(-starts_with("occipital")) %>% 
  dplyr::select(-contains("Rating")) %>% 
  dplyr::select(-contains("Source")) %>% 
  dplyr::select(-contains("Bogen")) %>% 
  dplyr::select(-contains("SoDe")) %>% 
  dplyr::select(-contains("P_post")) %>% 
  dplyr::select(-contains("RPQ")) %>% 
  dplyr::select(-contains("Spalte")) %>%
  dplyr::select(-contains("insgesamt")) %>%
  dplyr::select(-contains("Gesamt"))
```

```{r}
# renaming
tbi13<-rename(tbi13, id="ID", sex.kid="GenderJ", age.kid="AlterJ",
                age.cluster="Altersgruppe", education.mum="BildAb_Mutter",
                education.dad="BildAb_Vater", fam.situation="FamSit",
                pcsisr1301="Item1_phy_J_post",
                pcsisr1302="Item2_phy_J_post",
                pcsisr1303="Item3_phy_J_post",
                pcsisr1304="Item4_phy_J_post",
                pcsisr1305="Item5_phy_J_post",
                pcsisr1306="Item6_phy_J_post",
                pcsisr1307="Item7_phy_J_post",
                pcsisr1308="Item8_phy_J_post",
                pcsisr1309="Item9_em_J_post",
                pcsisr1310="Item10_em_J_post",
                pcsisr1311="Item11_em_J_post",
                pcsisr1312="Item12_em_J_post",
                pcsisr1313="Item13_kog_J_post",
                pcsisr1314="Item14_kog_J_post",
                pcsisr1315="Item15_kog_J_post",
                pcsisr1316="Item16_kog_J_post",
                pcsisr1317="Item17_kog_J_post",
                pcsisr1318="Item18_kog_J_post",
                pcsisr1319="Item19_fat_J_post",
                pcsisr1320="Item20_fat_J_post",
                pcsisr1321="Item21_fat_J_post",
                age.fam="AlterdesElternteils", submitdate="Testdatum2")
```

```{r}
# rounding age to integer
tbi13$age.kid<-signif(tbi13$age.kid, digits = 2)
```

```{r}
# back-up data
tbi13.1<-tbi13
```

# auxiliary variable

```{r}
items.pcsi13 <- paste("pcsisr13", c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10",
                                    "11", "12", "13", "14", "15", "16", "17", "18", "19", "20",
                                    "21"), sep = "")

physical.13 <- c("pcsisr1301", "pcsisr1302", "pcsisr1303", 
                "pcsisr1304", "pcsisr1305", "pcsisr1306", 
                "pcsisr1307","pcsisr1308")

emotional.13 <- c("pcsisr1309", "pcsisr1310", "pcsisr1311", "pcsisr1312")

cognitive.13 <- c("pcsisr1313", "pcsisr1314", "pcsisr1315", "pcsisr1316",
                  "pcsisr1317", "pcsisr1318")

fatigue.13 <- c("pcsisr1319", "pcsisr1320", "pcsisr1321")
```


```{r}
tbi13.1$missings = apply(tbi13.1, 1, function(x){sum(is.na(x))}) 
```

```{r}
table(tbi13.1$missings)
```

# Replace missing values with mean of the remaining items for tbi-data

```{r}
tbi13.1[tbi13.1$missings == 1, physical.13] = apply(tbi13.1[tbi13.1$missings == 1, physical.13], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(tbi13.1[tbi13.1$missings == 1, physical.13], na.rm = T)), x)))
```

```{r}
tbi13.1[tbi13.1$missings == 1, emotional.13] = apply(tbi13.1[tbi13.1$missings == 1, emotional.13], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(tbi13.1[tbi13.1$missings == 1, emotional.13], na.rm = T)), x)))
```

```{r}
tbi13.1[tbi13.1$missings == 1, cognitive.13] = apply(tbi13.1[tbi13.1$missings == 1, cognitive.13], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(tbi13.1[tbi13.1$missings == 1, cognitive.13], na.rm = T)), x)))
```

```{r}
tbi13.1[tbi13.1$missings == 1, fatigue.13] = apply(tbi13.1[tbi13.1$missings == 1, fatigue.13], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(tbi13.1[tbi13.1$missings == 1, fatigue.13], na.rm = T)), x)))
```

## Scales

```{r}
tbi13.1$pcsisr13.physical = apply(tbi13.1[physical.13],1,sum)
tbi13.1$pcsisr13.emotional = apply(tbi13.1[emotional.13],1,sum)
tbi13.1$pcsisr13.cognitive = apply(tbi13.1[cognitive.13],1,sum)
tbi13.1$pcsisr13.fatigue = apply(tbi13.1[fatigue.13],1,sum)
tbi13.1$pcsisr13.total = apply(tbi13.1[items.pcsi13],1,sum)
```

```{r}
write_csv(tbi13.1, file = "PCSI-SR13_TBI_imputed.csv")
save(tbi13.1, file = "PCSI-SR13_TBI_imputed.RData")
```

# data
## original data (0-6)

```{r}
# tbi
tbi13.2<-tbi13.1
```

```{r}
# healthy
dat.h2<-dat.f
```

## tricho data (0 = 0, 1 = 1-3, 2 = 4-6, c. Sady table 3)

```{r}
# back-up data
tbi13.tricho<-tbi13.1
dat.h.tricho<-dat.f
```

```{r}
# tbi
tbi13.tricho[, items.pcsi13]<-apply(tbi13.tricho[, items.pcsi13], 2,
                                    function (x) {ifelse (x == 0, 0,
                                                          ifelse(x == 1 | x == 2 | x == 3, 1, 2))})
```

```{r}
# healthy
dat.h.tricho[, items.pcsi13]<-apply(dat.h.tricho[, items.pcsi13], 2,
                                    function (x) {ifelse (x == 0, 0,
                                                          ifelse(x == 1 | x == 2 | x == 3, 1, 2))})
```

# merge tbi & healthy
## original data
```{r}
# subsetting
bet<-dat.h2 %>%
  dplyr::select(id, age.cluster, pcsisr1301:pcsisr1321)

# add identifications
bet$tbi<-1
tbi13.2$tbi<-2

bet$age.cluster<-as.numeric(bet$age.cluster)

# merging
tbi.pcsisr13<-bind_rows(bet, tbi13.2)
```

## tricho data
```{r}
# subsetting
bet2<-dat.h.tricho %>% 
  dplyr::select(id, age.cluster, pcsisr1301:pcsisr1321)

# add identifications
bet2$tbi<-1
tbi13.tricho$tbi<-2

bet2$age.cluster<-as.numeric(bet2$age.cluster)

# merging
tbi.pcsisr13.tricho<-bind_rows(bet2, tbi13.tricho)
```

# cfa model

```{r}
teen.model <- ' # measurement model
                    physical =~ pcsisr1301 + pcsisr1302 + pcsisr1303 + pcsisr1304 + pcsisr1305 +
                                pcsisr1306 + pcsisr1307 + pcsisr1308
                   emotional =~ pcsisr1309 + pcsisr1310 + pcsisr1311 + pcsisr1312
                   cognitive =~ pcsisr1313 + pcsisr1314 + pcsisr1315 + pcsisr1316 + pcsisr1317 +
                                pcsisr1318
                     fatigue =~ pcsisr1319 + pcsisr1320 + pcsisr1321
              '
```

# cfa tbi
## original data
```{r}
fit1 <- cfa(teen.model, data = tbi13.2, ordered = TRUE, std.lv = TRUE)
# variance-covariance matrix of the estimated parameters is not positive definite
```

```{r}
write.table(lavInspect(fit1, "vcov"), "PCSI_13_check_vcov_TBI_imputiert.csv", row.names = T, sep = ";")
summary(fit1)
```

## tricho data
```{r}
fit2 <- cfa(teen.model, data = tbi13.tricho, ordered = TRUE, std.lv = TRUE)
summary(fit2, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit2, c("chisq.scaled","df.scaled", "cfi.scaled", "tli.scaled","rmsea.scaled",
                           "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "srmr")) # good fit, except srmr
fitmeasures(fit2, "chisq.scaled")/fitmeasures(fit2, "df.scaled")
```

# cfa healthy
## original data
```{r}
fit3 <- cfa(teen.model, data = dat.h2, ordered = TRUE, std.lv = TRUE)
summary(fit3, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit3, c("chisq.scaled","df.scaled", "cfi.scaled", "tli.scaled","rmsea.scaled",
                           "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "srmr")) # good fit
fitmeasures(fit3, "chisq.scaled")/fitmeasures(fit3, "df.scaled")
```

## tricho data
```{r}
fit4 <- cfa(teen.model, data = dat.h.tricho, ordered = TRUE, std.lv = TRUE)
summary(fit4, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit4, c("chisq.scaled","df.scaled", "cfi.scaled", "tli.scaled","rmsea.scaled",
                           "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "srmr")) # good fit
fitmeasures(fit4, "chisq.scaled")/fitmeasures(fit4, "df.scaled")
```

# cfa mixed
## original data
```{r}
fit5 <- cfa(teen.model, data = tbi.pcsisr13, ordered = TRUE, std.lv = TRUE)
# variance-covariance matrix of the estimated parameters is not positive definite
```

```{r}
write.table(lavInspect(fit5, "vcov"), "PCSI_13_check_vcov_MIXED_imputiert.csv", row.names = T, sep = ";")
summary(fit5)
```

## tricho data
```{r}
fit6 <- cfa(teen.model, data = tbi.pcsisr13.tricho, ordered = TRUE, std.lv = TRUE)
summary(fit6, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit6, c("chisq.scaled","df.scaled", "cfi.scaled", "tli.scaled","rmsea.scaled",
                           "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "srmr")) # good fit
fitmeasures(fit6, "chisq.scaled")/fitmeasures(fit6, "df.scaled")
```

# MI tricho
## baseline
```{r}
# preparing a matrix for results
all.results.pcsisr13<-matrix(NA, nrow = 3, ncol = 9)
colnames(all.results.pcsisr13)<-c("chisq.scaled", "df.scaled", "pvalue.scaled", "rmsea.scaled",
                                  "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled",
                                  "cfi.scaled","tli.scaled", "srmr")
# baseline model
baseline <- measEq.syntax(configural.model = teen.model,
                           data = tbi.pcsisr13.tricho,
                           ordered = c("pcsisr1301", "pcsisr1302", "pcsisr1303", "pcsisr1304", "pcsisr1305", 
                                       "pcsisr1306", "pcsisr1307", "pcsisr1308", "pcsisr1309", "pcsisr1310",
                                       "pcsisr1311", "pcsisr1312", "pcsisr1313", "pcsisr1314", "pcsisr1315",
                                       "pcsisr1316", "pcsisr1317", "pcsisr1318", "pcsisr1319", "pcsisr1320",
                                       "pcsisr1321"),
                           parameterization = "delta", ID.fac = "std.lv",
                           ID.cat = "Wu.Estabrook.2016", group = "tbi",
                           group.equal = "configural")

summary(baseline)

# constraints
cat(as.character(baseline))

# as.character to submit to lavaan
model.baseline <- as.character(baseline)

# Fitting baseline model in lavaan via cfa function
fit.baseline <- cfa(model.baseline, data = tbi.pcsisr13.tricho, group = "tbi",
                     ordered = c("pcsisr1301", "pcsisr1302", "pcsisr1303", "pcsisr1304", "pcsisr1305", 
                                 "pcsisr1306", "pcsisr1307", "pcsisr1308", "pcsisr1309", "pcsisr1310",
                                 "pcsisr1311", "pcsisr1312", "pcsisr1313", "pcsisr1314", "pcsisr1315",
                                 "pcsisr1316", "pcsisr1317", "pcsisr1318", "pcsisr1319", "pcsisr1320",
                                 "pcsisr1321"), std.lv = TRUE)

# results
summary(fit.baseline)

# adding results to matrix
all.results.pcsisr13[1,]<-round(data.matrix(fitmeasures(fit.baseline,
                                                        fit.measures = c("chisq.scaled", "df.scaled", 
                                                                         "pvalue.scaled", "rmsea.scaled",
                                                                         "rmsea.ci.lower.scaled",
                                                                         "rmsea.ci.upper.scaled",
                                                                         "cfi.scaled","tli.scaled",
                                                                         "srmr"))),
                        digits=3)

fitmeasures(fit.baseline, "chisq.scaled")/fitmeasures(fit.baseline, "df.scaled")
```

## thresholds
```{r}
# thresholds model
prop4d <- measEq.syntax(configural.model = teen.model,
                        data = tbi.pcsisr13.tricho,
                        ordered = c("pcsisr1301", "pcsisr1302", "pcsisr1303", "pcsisr1304", "pcsisr1305", 
                                    "pcsisr1306", "pcsisr1307", "pcsisr1308", "pcsisr1309", "pcsisr1310",
                                    "pcsisr1311", "pcsisr1312", "pcsisr1313", "pcsisr1314", "pcsisr1315",
                                    "pcsisr1316", "pcsisr1317", "pcsisr1318", "pcsisr1319", "pcsisr1320",
                                    "pcsisr1321"),
                        parameterization = "delta", ID.fac = "std.lv",
                        ID.cat = "Wu.Estabrook.2016", group = "tbi",
                        group.equal = c("thresholds"))

model.prop4d <- as.character(prop4d)

# fitting into lavaan
fit.prop4d <- cfa(model.prop4d, data = tbi.pcsisr13.tricho, group = "tbi",
                  ordered = c("pcsisr1301", "pcsisr1302", "pcsisr1303", "pcsisr1304", "pcsisr1305", 
                              "pcsisr1306", "pcsisr1307", "pcsisr1308", "pcsisr1309", "pcsisr1310",
                              "pcsisr1311", "pcsisr1312", "pcsisr1313", "pcsisr1314", "pcsisr1315",
                              "pcsisr1316", "pcsisr1317", "pcsisr1318", "pcsisr1319", "pcsisr1320",
                              "pcsisr1321"), std.lv = TRUE)

# results
summary(fit.prop4d)

# adding results to matrix
all.results.pcsisr13[2,]<-round(data.matrix(fitmeasures(fit.prop4d,
                                                        fit.measures = c("chisq.scaled", "df.scaled", 
                                                                         "pvalue.scaled", "rmsea.scaled",
                                                                         "rmsea.ci.lower.scaled",
                                                                         "rmsea.ci.upper.scaled",
                                                                         "cfi.scaled","tli.scaled",
                                                                         "srmr"))),
                       digits=3)

fitmeasures(fit.prop4d, "chisq.scaled")/fitmeasures(fit.prop4d, "df.scaled")

# comparing the models
lavTestLRT(fit.baseline,fit.prop4d) # same df
```

## thresholds and loading invariance
```{r}
# thresholds and loading model
prop7d <- measEq.syntax(configural.model = teen.model,
                        data = tbi.pcsisr13.tricho,
                        ordered = c("pcsisr1301", "pcsisr1302", "pcsisr1303", "pcsisr1304", "pcsisr1305", 
                                    "pcsisr1306", "pcsisr1307", "pcsisr1308", "pcsisr1309", "pcsisr1310",
                                    "pcsisr1311", "pcsisr1312", "pcsisr1313", "pcsisr1314", "pcsisr1315",
                                    "pcsisr1316", "pcsisr1317", "pcsisr1318", "pcsisr1319", "pcsisr1320",
                                    "pcsisr1321"),
                        parameterization = "delta", ID.fac = "std.lv",
                        ID.cat = "Wu.Estabrook.2016", group = "tbi",
                        group.equal = c("thresholds", "loadings"))

model.prop7d <- as.character(prop7d)

# fitting into lavaan
fit.prop7d <- cfa(model.prop7d, data = tbi.pcsisr13.tricho, group = "tbi",
                  ordered = c("pcsisr1301", "pcsisr1302", "pcsisr1303", "pcsisr1304", "pcsisr1305", 
                              "pcsisr1306", "pcsisr1307", "pcsisr1308", "pcsisr1309", "pcsisr1310",
                              "pcsisr1311", "pcsisr1312", "pcsisr1313", "pcsisr1314", "pcsisr1315",
                              "pcsisr1316", "pcsisr1317", "pcsisr1318", "pcsisr1319", "pcsisr1320",
                              "pcsisr1321"), std.lv = TRUE)

# results
summary(fit.prop7d)

# adding results to matrix
all.results.pcsisr13[3,]<-round(data.matrix(fitmeasures(fit.prop7d,
                                                        fit.measures = c("chisq.scaled", "df.scaled", 
                                                                         "pvalue.scaled", "rmsea.scaled",
                                                                         "rmsea.ci.lower.scaled",
                                                                         "rmsea.ci.upper.scaled",
                                                                         "cfi.scaled","tli.scaled",
                                                                         "srmr"))),
                       digits=3)

fitmeasures(fit.prop7d, "chisq.scaled")/fitmeasures(fit.prop7d, "df.scaled")

# comparing the models
lavTestLRT(fit.prop4d, fit.prop7d) # significant, prop4d
```

# Comparison TBI vs. HEALTHY - thresholds and loadings vs. thresholds

```{r}
physical.pcsi13 <- c("Headache",
                     "Nausea",
                     "Balance problems",
                     "Dizziness",
                     "Visual problems (double vision, blurring)",
                     "Move in a clumsy manner",
                     "Sensitivity to light",
                     "Sensitivity to noise")

emotional.pcsi13 <- c("Irritability",
                      "Sadness",
                      "Nervousness",
                      "Feeling more emotional")

cognitive.pcsi13 <- c("Feeling mentally foggy",
                      "Difficulty concentrating",
                      "Difficulty remembering",
                      "Get confused with directions or tasks",
                      "Answer questions more slowly than usual",
                      "Feeling slowed down")

fatigue.pcsi13 <- c("Fatigue",
                    "Drowsiness",
                    "Sleep more than usual")

names.pcsi13 <- c(physical.pcsi13, emotional.pcsi13, cognitive.pcsi13, fatigue.pcsi13)
```

## difference thresholds and loadings model

```{r}
fitted_load_health <- 1-pnorm(inspect(fit.prop7d, "fitted")$`1`$th)
inspect(fit.prop7d, "fitted")
```

```{r}
fitted_load_TBI <- 1-pnorm(inspect(fit.prop7d, "fitted")$`2`$th)
```

```{r}
dif_fitted_load_B <- fitted_load_health - fitted_load_TBI # negative values indicate higher values in TBI sample (higher HRQoL)
```

## difference thresholds model

```{r}
fitted_load_health_A <- 1-pnorm(inspect(fit.prop4d, "fitted")$`1`$th)
```

```{r}
fitted_load_TBI_A <- 1-pnorm(inspect(fit.prop4d, "fitted")$`2`$th)
```

```{r}
dif_fitted_load_A <- fitted_load_health_A - fitted_load_TBI_A
```

## differnce between both

```{r}
dif_fitted_load <- dif_fitted_load_B - dif_fitted_load_A # higher values indicate higher differences in restrictive model and for healthy participants
```


### plots
```{r}
plot_health <- data.frame(Values = as.vector(dif_fitted_load_B),
                         Items = str_split(names(dif_fitted_load_B), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(dif_fitted_load_B), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load))
```

```{r}
plot_health_re <- reshape(plot_health,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_health_re) = c("Items", paste(c("T", "Diff"), rep(1:2, each = 2), sep = ""))
```

```{r}
plot_health_re$Sample <- 0
```

```{r}
plot_TBI <- data.frame(Values = as.vector(dif_fitted_load_A),
                         Items = str_split(names(dif_fitted_load_A), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(dif_fitted_load_A), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load))
```

```{r}
plot_TBI_re <- reshape(plot_TBI,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_TBI_re) = c("Items", paste(c("T", "Diff"), rep(1:2, each = 2), sep = ""))
```

```{r}
plot_TBI_re$Sample <- 1
```

```{r}
plot1 <- rbind.data.frame(plot_health_re, plot_TBI_re)
```

```{r}
plot1$Sample <- factor(plot1$Sample,
                       c(0,1),
                       c("Difference1", "Difference2"))
```

```{r}
tiff("Figure_Differences_imputed.tif", width = 7, height = 8, units = "in", res = 300)
layout(matrix(c(1,2,3), nrow = 1, ncol = 3, byrow = TRUE))

# labels
par(mar = c(3, 17, 4, 0))
plot.new()
plot.window(ylim = c(0, 21),
            xlim = c(-0.3, 0.3),
            yaxt = "n")
axis(2, c(length(names.pcsi13):1), names.pcsi13, las = 2, cex.axis = .95)

# T1
par(mar = c(3, 1, 4, 0))
plot(plot1$T1[plot1$Sample == "Difference1"],
     c(length(plot1$Items[plot1$Sample == "Difference1"]):1),
     xaxt = "n",
     yaxt = "n",
     ylim = c(0, 21),
     xlim = c(-0.3, 0.3),
     xlab = "",
     ylab = "",
     pch = 16,
     col = ifelse(plot1$Diff1[plot1$Sample == "Difference1"] > 0.05, "red", "black"))

abline(h = c(1:21), col = "lightgrey", lty = 3)
abline(v=0, col = "lightgrey")

points(plot1$T1[plot1$Sample == "Difference1"],
       c(length(plot1$Items[plot1$Sample == "Difference1"]):1),
       col = ifelse(plot1$Diff1[plot1$Sample == "Difference1"] > 0.05, "red", "black"))

points(plot1$T1[plot1$Sample == "Difference2"],
       c(length(plot1$Items[plot1$Sample == "Difference2"]):1),
       col = ifelse(plot1$Diff1[plot1$Sample == "Difference2"] > 0.05, "red", "black"))

axis(1, seq(-0.3, 0.3, 0.2), seq(-0.3, 0.3, 0.2))

title("Comparison: T1", adj = 0, line = 1)

segments(plot1$T1[plot1$Sample == "Difference1"],
         c(length(names.pcsi13):1),
         plot1$T1[plot1$Sample == "Difference2"],
         c(length(names.pcsi13):1),
         lty = 2,
         col = ifelse(plot1$Diff1[plot1$Sample == "Difference1"] > 0.05, "red", "gray"))

# T2
par(mar = c(3, 1, 4, 1))

plot(plot1$T2[plot1$Sample == "Difference1"],
     c(length(plot1$Items[plot1$Sample == "Difference1"]):1),
     xaxt = "n",
     yaxt = "n",
     ylim = c(0, 21),
     xlim = c(-0.3, 0.3),
     xlab = "",
     ylab = "",
     pch = 16,
     col = ifelse(plot1$Diff2[plot1$Sample == "Difference1"] > 0.05, "red", "black"))

abline(h = c(1:21), col = "lightgrey", lty = 3)
abline(v=0, col = "lightgrey")

points(plot1$T2[plot1$Sample == "Difference1"],
       c(length(plot1$Items[plot1$Sample == "Difference1"]):1),
       col = ifelse(plot1$Diff2[plot1$Sample == "Difference1"] > 0.05, "red", "black"))

points(plot1$T2[plot1$Sample == "Difference2"],
       c(length(plot1$Items[plot1$Sample == "Difference2"]):1),
       col = ifelse(plot1$Diff2[plot1$Sample == "Differnce2"] > 0.05, "red", "black"))

axis(1, seq(-0.3, 0.3,0.2), seq(-0.3, 0.3, 0.2))

title ("T2", adj = 0, line = 1)

segments(plot1$T2[plot1$Sample == "Difference1"], 
         c(length(names.pcsi13):1), 
         plot1$T2[plot1$Sample == "Difference2"], 
         c(length(names.pcsi13):1),
         lty = 2,
         col = ifelse(plot1$Diff2[plot1$Sample == "Difference1"] > 0.05, "red", "gray"))

legend("bottomright",
       bty = "n",
       pch = c(16, 1),
       lty = 3,
       col = c(rep(1,2), 2),
       c("Difference thresholds and loadings",
         "Difference thresholds",
         "difference > 5%"))
dev.off()
```

