---
title: "07C_MI_metric_imputiert"
output: html_document
date: "2023-03-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages

```{r}
library(tidyverse)
library(lavaan)
library(semTools)
library(dplyr)
library(haven)
library(Hmisc)
```

# import data
```{r}
tbi13<-read_sav("Datensatz_3_Masterarbeit_DT_22_23.sav")
load("data_final.Rdata")
```

## preparation of tbi-data
```{r}
# back-up data
tbi13.1<-tbi13
```

```{r}
# removing unnecessary columns
tbi13.1<-subset(tbi13.1) %>% 
  dplyr::select(-ends_with("prae")) %>% 
  dplyr::select(-contains("RAPID")) %>% 
  dplyr::select(-c("Laufende_Nummer", "Zentrum", "TestdatumJ", "TestdatumE", "Schweregrad", "KOSCHI",
                   "BesVer_Mutter", "BesVer_Vater", "stationary", "ambulatory", "direct",
                   "indirect", "multilingual", "Testdatum.Untersucher")) %>% 
  dplyr::select(-contains("SHT")) %>% 
  dplyr::select(-ends_with("tri")) %>% 
  dplyr::select(-starts_with("Low")) %>% 
  dplyr::select(-starts_with("U")) %>%
  dplyr::select(-starts_with("High")) %>%
  dplyr::select(-starts_with("frontal")) %>%
  dplyr::select(-starts_with("temporal")) %>% 
  dplyr::select(-starts_with("parietal")) %>% 
  dplyr::select(-starts_with("occipital")) %>% 
  dplyr::select(-contains("Rating")) %>% 
  dplyr::select(-contains("Source")) %>% 
  dplyr::select(-contains("Bogen")) %>% 
  dplyr::select(-contains("SoDe")) %>% 
  dplyr::select(-contains("P_post")) %>% 
  dplyr::select(-contains("RPQ")) %>% 
  dplyr::select(-contains("Spalte")) %>%
  dplyr::select(-contains("insgesamt")) %>%
  dplyr::select(-contains("Gesamt"))
```

```{r}
# renaming
tbi13.1<-rename(tbi13.1, id="ID", sex.kid="GenderJ", age.kid="AlterJ",
                age.cluster="Altersgruppe", education.mum="BildAb_Mutter",
                education.dad="BildAb_Vater", fam.situation="FamSit",
                pcsisr1301="Item1_phy_J_post",
                pcsisr1302="Item2_phy_J_post",
                pcsisr1303="Item3_phy_J_post",
                pcsisr1304="Item4_phy_J_post",
                pcsisr1305="Item5_phy_J_post",
                pcsisr1306="Item6_phy_J_post",
                pcsisr1307="Item7_phy_J_post",
                pcsisr1308="Item8_phy_J_post",
                pcsisr1309="Item9_em_J_post",
                pcsisr1310="Item10_em_J_post",
                pcsisr1311="Item11_em_J_post",
                pcsisr1312="Item12_em_J_post",
                pcsisr1313="Item13_kog_J_post",
                pcsisr1314="Item14_kog_J_post",
                pcsisr1315="Item15_kog_J_post",
                pcsisr1316="Item16_kog_J_post",
                pcsisr1317="Item17_kog_J_post",
                pcsisr1318="Item18_kog_J_post",
                pcsisr1319="Item19_fat_J_post",
                pcsisr1320="Item20_fat_J_post",
                pcsisr1321="Item21_fat_J_post",
                age.fam="AlterdesElternteils", submitdate="Testdatum2")
```

```{r}
# rounding age to integer
tbi13.1$age.kid<-signif(tbi13.1$age.kid, digits = 2)
```

# auxiliary variable

```{r}
items.pcsi13 <- paste("pcsisr13", c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10",
                                    "11", "12", "13", "14", "15", "16", "17", "18", "19", "20",
                                    "21"), sep = "")

physical.13 <- c("pcsisr1301", "pcsisr1302", "pcsisr1303", 
                "pcsisr1304", "pcsisr1305", "pcsisr1306", 
                "pcsisr1307","pcsisr1308")

emotional.13 <- c("pcsisr1309", "pcsisr1310", "pcsisr1311", "pcsisr1312")

cognitive.13 <- c("pcsisr1313", "pcsisr1314", "pcsisr1315", "pcsisr1316",
                  "pcsisr1317", "pcsisr1318")

fatigue.13 <- c("pcsisr1319", "pcsisr1320", "pcsisr1321")
```


```{r}
tbi13.1$missings = apply(tbi13.1, 1, function(x){sum(is.na(x))}) 
```

```{r}
table(tbi13.1$missings)
```

# Replace missing values with mean of the remaining items for tbi-data

```{r}
tbi13.1[,physical.13] <- impute(tbi13.1[,physical.13], mean)
tbi13.1[,emotional.13] <- impute(tbi13.1[,emotional.13], mean)
tbi13.1[,cognitive.13] <- impute(tbi13.1[,cognitive.13], mean)
tbi13.1[,fatigue.13] <- impute(tbi13.1[,fatigue.13], mean)
```

## Scales

```{r}
tbi13.1$pcsisr13.physical = apply(tbi13.1[physical.13],1,sum)
tbi13.1$pcsisr13.emotional = apply(tbi13.1[emotional.13],1,sum)
tbi13.1$pcsisr13.cognitive = apply(tbi13.1[cognitive.13],1,sum)
tbi13.1$pcsisr13.fatigue = apply(tbi13.1[fatigue.13],1,sum)
tbi13.1$pcsisr13.total = apply(tbi13.1[items.pcsi13],1,sum)
```

```{r}
library(table1)

table1(~pcsisr1301 + pcsisr1302 + pcsisr1303 + pcsisr1304 + pcsisr1305 +
         pcsisr1306 + pcsisr1307 + pcsisr1308 +
       pcsisr1309 + pcsisr1310 + pcsisr1311 + pcsisr1312 +
       pcsisr1313 + pcsisr1314 + pcsisr1315 + pcsisr1316 + pcsisr1317 +
         pcsisr1318 + pcsisr1319 + pcsisr1320 + pcsisr1321, data = tbi13.1)
```

# data
## original data (0-6)

```{r}
# tbi
tbi13.2<-tbi13.1
```

```{r}
# healthy
dat.h2<-dat.f
```

# merge tbi & healthy
## original data
```{r}
# subsetting
bet<-dat.h2 %>%
  dplyr::select(id, age.cluster, pcsisr1301:pcsisr1321)

# add identifications
bet$tbi<-1
tbi13.2$tbi<-2

bet$age.cluster<-as.numeric(bet$age.cluster)

# merging
tbi.pcsisr13<-bind_rows(bet, tbi13.2)
```

# cfa model

```{r}
teen.model <- ' # measurement model
                    physical =~ pcsisr1301 + pcsisr1302 + pcsisr1303 + pcsisr1304 + pcsisr1305 +
                                pcsisr1306 + pcsisr1307 + pcsisr1308
                   emotional =~ pcsisr1309 + pcsisr1310 + pcsisr1311 + pcsisr1312
                   cognitive =~ pcsisr1313 + pcsisr1314 + pcsisr1315 + pcsisr1316 + pcsisr1317 +
                                pcsisr1318
                     fatigue =~ pcsisr1319 + pcsisr1320 + pcsisr1321
              '
```

# cfa tbi
## original data
```{r}
fit1 <- cfa(teen.model, data = tbi13.2, std.lv = TRUE)
summary(fit1, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit1, c("chisq","df", "pvalue", "cfi", "tli","rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))
fitmeasures(fit1, "chisq")/fitmeasures(fit1, "df")
```

# cfa healthy
## original data
```{r}
fit3 <- cfa(teen.model, data = dat.h2, std.lv = TRUE)
summary(fit3, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit3, c("chisq","df", "pvalue", "cfi", "tli","rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))
fitmeasures(fit3, "chisq")/fitmeasures(fit3, "df")
```

# cfa mixed
## original data
```{r}
fit5 <- cfa(teen.model, data = tbi.pcsisr13, std.lv = TRUE)
summary(fit5, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit5, c("chisq","df", "pvalue", "cfi", "tli","rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))
fitmeasures(fit5, "chisq")/fitmeasures(fit5, "df")
```

# MI
## configural invariance
```{r}
# preparing a matrix for results
all.results.pcsisr13<-matrix(NA, nrow = 3, ncol = 9)
colnames(all.results.pcsisr13)<-c("chisq", "df", "pvalue", "rmsea",
                                  "rmsea.ci.lower", "rmsea.ci.upper",
                                  "cfi","tli", "srmr")

# Fitting configural model in lavaan via cfa function
fit.configural <- cfa(teen.model, data = tbi.pcsisr13, group = "tbi", std.lv = TRUE)

# results
summary(fit.configural)

# adding results to matrix
all.results.pcsisr13[1,]<-round(data.matrix(fitmeasures(fit.configural,
                                                        fit.measures = c("chisq", "df", 
                                                                         "pvalue", "rmsea",
                                                                         "rmsea.ci.lower",
                                                                         "rmsea.ci.upper",
                                                                         "cfi","tli",
                                                                         "srmr"))),
                        digits=3)

fitmeasures(fit.configural, "chisq")/fitmeasures(fit.configural, "df")
```

## weak invariance
```{r}
# fitting into lavaan
fit.weak <- cfa(teen.model, data = tbi.pcsisr13, group = "tbi", group.equal = "loadings",
                std.lv = TRUE)

# results
summary(fit.weak)

# adding results to matrix
all.results.pcsisr13[2,]<-round(data.matrix(fitmeasures(fit.weak,
                                                        fit.measures = c("chisq", "df", 
                                                                         "pvalue", "rmsea",
                                                                         "rmsea.ci.lower",
                                                                         "rmsea.ci.upper",
                                                                         "cfi","tli",
                                                                         "srmr"))),
                       digits=3)

fitmeasures(fit.weak, "chisq")/fitmeasures(fit.weak, "df")

# comparing the models
lavTestLRT(fit.configural,fit.weak) # significant, baseline
```

## strong invariance
```{r}
# fitting into lavaan
fit.strong <- cfa(teen.model, data = tbi.pcsisr13, group = "tbi",
                  group.equal = c("loadings", "intercepts"),
                  std.lv = TRUE)

# results
summary(fit.strong)

# adding results to matrix
all.results.pcsisr13[3,]<-round(data.matrix(fitmeasures(fit.strong,
                                                        fit.measures = c("chisq", "df", 
                                                                         "pvalue", "rmsea",
                                                                         "rmsea.ci.lower",
                                                                         "rmsea.ci.upper",
                                                                         "cfi","tli",
                                                                         "srmr"))),
                       digits=3)

fitmeasures(fit.strong, "chisq")/fitmeasures(fit.strong, "df")

# comparing the models
lavTestLRT(fit.weak, fit.strong) # significant, strong
lavTestLRT(fit.configural, fit.weak, fit.strong)
```

# Comparison TBI vs. HEALTHY

```{r}
physical.pcsi13 <- c("Headache",
                     "Nausea",
                     "Balance problems",
                     "Dizziness",
                     "Visual problems (double vision, blurring)",
                     "Move in a clumsy manner",
                     "Sensitivity to light",
                     "Sensitivity to noise")

emotional.pcsi13 <- c("Irritability",
                      "Sadness",
                      "Nervousness",
                      "Feeling more emotional")

cognitive.pcsi13 <- c("Feeling mentally foggy",
                      "Difficulty concentrating",
                      "Difficulty remembering",
                      "Get confused with directions or tasks",
                      "Answer questions more slowly than usual",
                      "Feeling slowed down")

fatigue.pcsi13 <- c("Fatigue",
                    "Drowsiness",
                    "Sleep more than usual")

names.pcsi13 <- c(physical.pcsi13, emotional.pcsi13, cognitive.pcsi13, fatigue.pcsi13)
```

## fit.weak

```{r}
fitted_load_health <- 1-pnorm(inspect(fit.weak, "fitted")$`1`$mean)
inspect(fit.weak, "fitted")
```

```{r}
fitted_load_TBI <- 1-pnorm(inspect(fit.weak, "fitted")$`2`$mean)
```

```{r}
dif_fitted_load <- fitted_load_health - fitted_load_TBI
```

## plots
```{r}
plot_health <- data.frame(Values = as.vector(fitted_load_health),
                         Items = str_split(names(fitted_load_health), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(fitted_load_health), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load))
```

```{r}
plot_health_re <- reshape(plot_health,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_health_re) = c("Items", paste(c("Mean", "Diff"), #rep(1:12, each = 2),
                                         sep = ""))
```

```{r}
plot_health_re$Sample <- 0
```

```{r}
plot_TBI <- data.frame(Values = as.vector(fitted_load_TBI),
                         Items = str_split(names(fitted_load_TBI), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(fitted_load_TBI), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load))
```

```{r}
plot_TBI_re <- reshape(plot_TBI,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_TBI_re) = c("Items", paste(c("Mean", "Diff"), #rep(1:2, each = 2),
                                      sep = ""))
```

```{r}
plot_TBI_re$Sample <- 1
```

```{r}
plot1 <- rbind.data.frame(plot_health_re, plot_TBI_re)
```

```{r}
plot1$Sample <- factor(plot1$Sample,
                       c(0,1),
                       c("general population", "TBI"))
```

```{r}
tiff("FigureA1_metric_imputiert.tif", width = 7, height = 12, units = "in", res = 300)
layout(matrix(c(1,2), nrow = 1, ncol = 2, byrow = TRUE))

# labels
par(mar = c(3, 17, 4, 0))
plot.new()
plot.window(ylim = c(0, 21),
            xlim = c(0, 1),
            yaxt = "n")
axis(2, c(length(names.pcsi13):1), names.pcsi13, las = 2, cex.axis = .95)

# T1
par(mar = c(3, 1, 4, 1))
plot(plot1$Mean[plot1$Sample == "general population"],
     c(length(plot1$Items[plot1$Sample == "general population"]):1),
     xaxt = "n",
     yaxt = "n",
     ylim = c(0, 21),
     xlim = c(0, 1),
     xlab = "",
     ylab = "",
     pch = 16,
     col = ifelse(plot1$Diff1[plot1$Sample == "general population"] > 0.05, "red", "black"))

abline(h = c(1:21), col = "lightgrey", lty = 3)

points(plot1$Mean[plot1$Sample == "general population"],
       c(length(plot1$Items[plot1$Sample == "general population"]):1),
       col = ifelse(plot1$Diff[plot1$Sample == "general population"] > 0.05, "red", "black"),
       pch = 16)

points(plot1$Mean[plot1$Sample == "TBI"],
       c(length(plot1$Items[plot1$Sample == "TBI"]):1),
       col = ifelse(plot1$Diff[plot1$Sample == "TBI"] > 0.05, "red", "black"))

axis(1, seq(0, 1, 0.2), seq(0, 1, 0.2))

title("Comparison: Means weak invariance", adj = 0, line = 1)

segments(plot1$Mean[plot1$Sample == "general population"],
         c(length(names.pcsi13):1),
         plot1$Mean[plot1$Sample == "TBI"],
         c(length(names.pcsi13):1),
         lty = 2,
         col = ifelse(plot1$Diff[plot1$Sample == "general population"] > 0.05, "red", "gray"))

legend("bottomright",
       bty = "n",
       pch = c(16, 1),
       lty = 3,
       col = c(rep(1,2), 2),
       c("general population sample",
         "TBI sample",
         "difference > 5%"))
dev.off()
```

## fit.strong

```{r}
fitted_load_health2 <- 1-pnorm(inspect(fit.strong, "fitted")$`1`$mean)
inspect(fit.strong, "fitted")
```

```{r}
fitted_load_TBI2 <- 1-pnorm(inspect(fit.strong, "fitted")$`2`$mean)

fitted.base<-1-pnorm(inspect(fit.configural, "fitted")$`2`$mean)
```

```{r}
dif_fitted_load2 <- fitted_load_health2 - fitted_load_TBI2
```

## plots
```{r}
plot_health2 <- data.frame(Values = as.vector(fitted_load_health2),
                         Items = str_split(names(fitted_load_health2), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(fitted_load_health2), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load2))
```

```{r}
plot_health_re2 <- reshape(plot_health2,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_health_re2) = c("Items", paste(c("Mean", "Diff"), #rep(1:12, each = 2),
                                         sep = ""))
```

```{r}
plot_health_re2$Sample <- 0
```

```{r}
plot_TBI2 <- data.frame(Values = as.vector(fitted_load_TBI2),
                         Items = str_split(names(fitted_load_TBI2), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(fitted_load_TBI2), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load2))
```

```{r}
plot_TBI_re2 <- reshape(plot_TBI2,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_TBI_re2) = c("Items", paste(c("Mean", "Diff"), #rep(1:2, each = 2),
                                      sep = ""))
```

```{r}
plot_TBI_re2$Sample <- 1
```

```{r}
plot2 <- rbind.data.frame(plot_health_re2, plot_TBI_re2)
```

```{r}
plot2$Sample <- factor(plot2$Sample,
                       c(0,1),
                       c("general population", "TBI"))
```

```{r}
tiff("FigureA2_metric_imputiert.tif", width = 7, height = 12, units = "in", res = 300)
layout(matrix(c(1,2), nrow = 1, ncol = 2, byrow = TRUE))

# labels
par(mar = c(3, 17, 4, 0))
plot.new()
plot.window(ylim = c(0, 21),
            xlim = c(0, 1),
            yaxt = "n")
axis(2, c(length(names.pcsi13):1), names.pcsi13, las = 2, cex.axis = .95)

# T1
par(mar = c(3, 1, 4, 1))
plot(plot2$Mean[plot2$Sample == "general population"],
     c(length(plot2$Items[plot2$Sample == "general population"]):1),
     xaxt = "n",
     yaxt = "n",
     ylim = c(0, 21),
     xlim = c(0, 1),
     xlab = "",
     ylab = "",
     pch = 16,
     col = ifelse(plot2$Diff1[plot2$Sample == "general population"] > 0.05, "red", "black"))

abline(h = c(1:21), col = "lightgrey", lty = 3)

points(plot2$Mean[plot2$Sample == "general population"],
       c(length(plot2$Items[plot2$Sample == "general population"]):1),
       col = ifelse(plot2$Diff[plot2$Sample == "general population"] > 0.05, "red", "black"),
       pch = 16)

points(plot2$Mean[plot2$Sample == "TBI"],
       c(length(plot2$Items[plot2$Sample == "TBI"]):1),
       col = ifelse(plot2$Diff[plot2$Sample == "TBI"] > 0.05, "red", "black"))

axis(1, seq(0, 1, 0.2), seq(0, 1, 0.2))

title("Comparison: Means strong invariance", adj = 0, line = 1)

segments(plot2$Mean[plot2$Sample == "general population"],
         c(length(names.pcsi13):1),
         plot2$Mean[plot2$Sample == "TBI"],
         c(length(names.pcsi13):1),
         lty = 2,
         col = ifelse(plot2$Diff[plot2$Sample == "general population"] > 0.05, "red", "gray"))

legend("bottomright",
       bty = "n",
       pch = c(16, 1),
       lty = 3,
       col = c(rep(1,2), 2),
       c("general population sample",
         "TBI sample",
         "difference > 5%"))
dev.off()
```

## fit.weak quer

```{r}
fitted_load_health <- 1-pnorm(inspect(fit.weak, "fitted")$`1`$mean)
inspect(fit.weak, "fitted")
```

```{r}
fitted_load_TBI <- 1-pnorm(inspect(fit.weak, "fitted")$`2`$mean)
```

```{r}
dif_fitted_load <- fitted_load_health - fitted_load_TBI
```

## plots
```{r}
plot_health <- data.frame(Values = as.vector(fitted_load_health),
                         Items = str_split(names(fitted_load_health), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(fitted_load_health), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load))
```

```{r}
plot_health_re <- reshape(plot_health,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_health_re) = c("Items", paste(c("Mean", "Diff"), #rep(1:12, each = 2),
                                         sep = ""))
```

```{r}
plot_health_re$Sample <- 0
```

```{r}
plot_TBI <- data.frame(Values = as.vector(fitted_load_TBI),
                         Items = str_split(names(fitted_load_TBI), "\\|", 2, simplify = TRUE)[,1],
                         Thresholds = str_split(names(fitted_load_TBI), "\\|", 2, simplify = TRUE)[,2],
                         Diff = as.vector(dif_fitted_load))
```

```{r}
plot_TBI_re <- reshape(plot_TBI,
        timevar = "Thresholds",
        idvar = "Items",
        direction = "wide")

names(plot_TBI_re) = c("Items", paste(c("Mean", "Diff"), #rep(1:2, each = 2),
                                      sep = ""))
```

```{r}
plot_TBI_re$Sample <- 1
```

```{r}
plot1 <- rbind.data.frame(plot_health_re, plot_TBI_re)
```

```{r}
plot1$Sample <- factor(plot1$Sample,
                       c(0,1),
                       c("general population", "TBI"))
```

```{r}
tiff("FigureA1_metric_imputiert.tif", width = 7, height = 12, units = "in", res = 300)
layout(matrix(c(1,2), nrow = 1, ncol = 2, byrow = TRUE))

# labels
par(mar = c(3, 17, 4, 0))
plot.new()
plot.window(ylim = c(0, 21),
            xlim = c(0, 1),
            yaxt = "n")
axis(2, c(length(names.pcsi13):1), names.pcsi13, las = 2, cex.axis = .95)

# T1
par(mar = c(3, 1, 4, 1))
plot(plot1$Mean[plot1$Sample == "general population"],
     c(length(plot1$Items[plot1$Sample == "general population"]):1),
     xaxt = "n",
     yaxt = "n",
     ylim = c(0, 21),
     xlim = c(0, 1),
     xlab = "",
     ylab = "",
     pch = 16,
     col = ifelse(plot1$Diff1[plot1$Sample == "general population"] > 0.05, "red", "black"))

abline(h = c(1:21), col = "lightgrey", lty = 3)

points(plot1$Mean[plot1$Sample == "general population"],
       c(length(plot1$Items[plot1$Sample == "general population"]):1),
       col = ifelse(plot1$Diff[plot1$Sample == "general population"] > 0.05, "red", "black"))

points(plot1$Mean[plot1$Sample == "TBI"],
       c(length(plot1$Items[plot1$Sample == "TBI"]):1),
       col = ifelse(plot1$Diff[plot1$Sample == "TBI"] > 0.05, "red", "black"))

axis(1, seq(0, 1, 0.2), seq(0, 1, 0.2))

title("Comparison: Means weak invariance", adj = 0, line = 1)

segments(plot1$Mean[plot1$Sample == "general population"],
         c(length(names.pcsi13):1),
         plot1$Mean[plot1$Sample == "TBI"],
         c(length(names.pcsi13):1),
         lty = 2,
         col = ifelse(plot1$Diff[plot1$Sample == "general population"] > 0.05, "red", "gray"))

legend("bottomright",
       bty = "n",
       pch = c(16, 1),
       lty = 3,
       col = c(rep(1,2), 2),
       c("general population sample",
         "TBI sample",
         "difference > 5%"))
dev.off()
```