---
title: "06A_MI_imputiert"
output: html_document
date: "2023-03-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages

```{r}
library(dplyr)
library(tidyverse)
library(lavaan)
library(semTools)
library(table1)
```


# TBI-sample
## import data
```{r}
pcsi8.1.new<-read.csv2("PCSI_kids_new_leo.csv", sep = ";", header = T)
```


## preparation of tbi-data
```{r}
# removing unnecessary columns
pcsi8.1.new<-subset(pcsi8.1.new) %>% 
  dplyr::select(-ends_with("prae")) %>% 
  dplyr::select(-contains("RAPID")) %>% 
  dplyr::select(-c("Testdatum", "Gender_K", "Alter", "Schweregrad", "Sonstige.Erkrankungen",
                   "Anmerkungen")) %>% 
  dplyr::select(-contains("Gesamt"))
```

```{r}
# renaming
pcsi8.1.new<-rename(pcsi8.1.new, id="ID", age.cluster="Altersgruppe", 
                pcsisr801="Item1_phy_C_post",
                pcsisr802="Item2_phy_C_post", 
                pcsisr803="Item3_phy_C_post", 
                pcsisr804="Item4_phy_C_post",
                pcsisr805="Item5_phy_C_post", 
                pcsisr806="Item6_phy_C_post", 
                pcsisr807="Item7_phy_C_post",
                pcsisr808="Item8_phy_C_post", 
                pcsisr809="Item9_em_C_post", 
                pcsisr810="Item10_em_C_post",
                pcsisr811="Item11_em_C_post", 
                pcsisr812="Item12_kog_C_post", 
                pcsisr813="Item13_kog_C_post",
                pcsisr814="Item14_kog_C_post", 
                pcsisr815="Item15_kog_C_post", 
                pcsisr816="Item16_fat_C_post",
                pcsisr817="Item17_fat_C_post")
```

```{r}
which(pcsi8.1.new == 99 | pcsi8.1.new == "ND" | pcsi8.1.new == "NC", arr.ind = TRUE)
# row/column: 35/3, 37/8, 53/13, 131/15, 9/19

pcsi8.1.new[35,3]
pcsi8.1.new[37,8]
pcsi8.1.new[53,13]
pcsi8.1.new[131,15]
pcsi8.1.new[9,19]

pcsi8.1.new[pcsi8.1.new == 99 | pcsi8.1.new == "ND" | pcsi8.1.new == "NC"]<-NA

# check
pcsi8.1.new[35,3]
pcsi8.1.new[37,8]
pcsi8.1.new[53,13]
pcsi8.1.new[131,15]
pcsi8.1.new[9,19]
```

```{r}
which(pcsi8.1.new == "ß", arr.ind = TRUE) # row 82, column 5
pcsi8.1.new[82,5]
pcsi8.1.new[pcsi8.1.new == "ß"]<-0
pcsi8.1.new[82,5]
pcsi8.1.new$pcsisr803<-as.integer(pcsi8.1.new$pcsisr803)
```

```{r}
# back-up
pcsi8.1<-pcsi8.1.new
```

## auxiliary variables

```{r}
physical.8 <- c("pcsisr801", "pcsisr802", "pcsisr803", 
                "pcsisr804", "pcsisr805", "pcsisr806", 
                "pcsisr807","pcsisr808")

emotional.8 <- c("pcsisr809", "pcsisr810", "pcsisr811")

cognitive.8 <- c("pcsisr812", "pcsisr813", "pcsisr814", "pcsisr815")

fatigue.8 <- c("pcsisr816", "pcsisr817")

total.8 <- c(physical.8, emotional.8, cognitive.8, fatigue.8)
```

```{r}
pcsi8.1$missings = apply(pcsi8.1, 1, function(x){sum(is.na(x))}) 
```

```{r}
table(pcsi8.1$missings)
```

## Replace missing values with mean of the remaining items

```{r}
pcsi8.1[pcsi8.1$missings == 1, physical.8] = apply(pcsi8.1[pcsi8.1$missings == 1, physical.8], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(pcsi8.1[pcsi8.1$missings == 1, physical.8], na.rm = T)), x)))
```

```{r}
pcsi8.1[pcsi8.1$missings == 1, emotional.8] = apply(pcsi8.1[pcsi8.1$missings == 1, emotional.8], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(pcsi8.1[pcsi8.1$missings == 1, emotional.8], na.rm = T)), x)))
```

```{r}
pcsi8.1[pcsi8.1$missings == 1, cognitive.8] = apply(pcsi8.1[pcsi8.1$missings == 1, cognitive.8], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(pcsi8.1[pcsi8.1$missings == 1, cognitive.8], na.rm = T)), x)))
```

```{r}
pcsi8.1[pcsi8.1$missings == 1, fatigue.8] = apply(pcsi8.1[pcsi8.1$missings == 1, fatigue.8], 2, 
      function(x)(ifelse(is.na(x) == T, round(rowMeans(pcsi8.1[pcsi8.1$missings == 1, fatigue.8], na.rm = T)), x)))
```

## Scales

```{r}
pcsi8.1$pcsisr8.physical = apply(pcsi8.1[physical.8],1,sum)
pcsi8.1$pcsisr8.emotional = apply(pcsi8.1[emotional.8],1,sum)
pcsi8.1$pcsisr8.cognitive = apply(pcsi8.1[cognitive.8],1,sum)
pcsi8.1$pcsisr8.fatigue = apply(pcsi8.1[fatigue.8],1,sum)
pcsi8.1$pcsisr8.total = apply(pcsi8.1[total.8],1,sum)
```


```{r}
# back-up data
pcsi8.2 <- pcsi8.1
```

## response patterns
```{r}
table1(~ factor(pcsisr801) + factor(pcsisr802) + factor(pcsisr803) +
         factor(pcsisr804) + factor(pcsisr805) + factor(pcsisr806) +
         factor(pcsisr807) + factor(pcsisr808) + factor(pcsisr809) +
         factor(pcsisr810) + factor(pcsisr811) + factor(pcsisr812) +
         factor(pcsisr813) + factor(pcsisr814) + factor(pcsisr815) +
         factor(pcsisr816) + factor(pcsisr817), data = pcsi8.2)

# all response categories are occupied
```

## CFA model
```{r}
eight.model <- ' # measurement model
                   physical =~ pcsisr801 + 
                               pcsisr802 + 
                               pcsisr803 + 
                               pcsisr804 + 
                               pcsisr805 + 
                               pcsisr806 +
                               pcsisr807 + 
                               pcsisr808
                               
                  emotional =~ pcsisr809 + 
                               pcsisr810 + 
                               pcsisr811
                               
                  cognitive =~ pcsisr812 + 
                               pcsisr813 + 
                               pcsisr814 + 
                               pcsisr815
                               
                    fatigue =~ pcsisr816 + 
                               pcsisr817
                               '
```

## CFA
```{r}
fit.pcsi8.o <- cfa(eight.model, data = pcsi8.2, ordered = TRUE, std.lv = T)
# covariance matrix of latent variables is not positive definite
```

```{r}
lavInspect(fit.pcsi8.o, "cov.lv")
```

```{r}
summary(fit.pcsi8.o, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit.pcsi8.o, c("chisq.scaled","df.scaled", "cfi.scaled", "tli.scaled","rmsea.scaled",
                           "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "srmr"))
# good model fit
fitmeasures(fit.pcsi8.o, "chisq.scaled")/fitmeasures(fit.pcsi8.o, "df.scaled")
```


# HEALTHY sample
## import data
```{r}
load("data_final.RData")
```

## CFA
```{r}
fit.pcsi8.h <- cfa(eight.model, data = dat.f, ordered = TRUE, std.lv = TRUE)
summary(fit.pcsi8.h, fit.measures = TRUE, standardized = TRUE)
fitmeasures(fit.pcsi8.h, c("chisq.scaled","df.scaled", "cfi.scaled", "tli.scaled","rmsea.scaled",
                           "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "srmr"))
# good model fit
fitmeasures(fit.pcsi8.h, "chisq.scaled")/fitmeasures(fit.pcsi8.h, "df.scaled")
```


# MIXED sample
## preparation
```{r}
# subsetting
bet1<-dat.f %>% 
  dplyr::select(id, age.cluster, pcsisr801:pcsisr817)

# add identifications
bet1$tbi<-1
pcsi8.2$tbi<-2

bet1$age.cluster<-as.numeric(bet1$age.cluster)

# merging
tbi.pcsisr8<-bind_rows(bet1, pcsi8.2)
```

## CFA
```{r}
fit.pcsi8.mix.o <- cfa(eight.model, data = tbi.pcsisr8, ordered = TRUE, std.lv = TRUE)

summary(fit.pcsi8.mix.o, fit.measures = TRUE, standardized = TRUE)

fitmeasures(fit.pcsi8.mix.o, c("chisq.scaled","df.scaled", "cfi.scaled", "tli.scaled","rmsea.scaled",
                           "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled", "srmr")) # good model fit

fitmeasures(fit.pcsi8.mix.o, "chisq.scaled")/fitmeasures(fit.pcsi8.mix.o, "df.scaled")
```


# measurement invariance: original data, original model
## Baseline model

```{r}
# preparing a matrix for results
all.results.pcsisr8<-matrix(NA, nrow = 3, ncol = 9)
colnames(all.results.pcsisr8)<-c("chisq.scaled", "df.scaled", "pvalue.scaled", "rmsea.scaled",
                                 "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled",
                                 "cfi.scaled","tli.scaled", "srmr")

# baseline model
baseline <- measEq.syntax(configural.model = eight.model,
                           data = tbi.pcsisr8,
                           ordered = c("pcsisr801", "pcsisr802", "pcsisr803", "pcsisr804", "pcsisr805" , 
                                       "pcsisr806", "pcsisr807", "pcsisr808", "pcsisr809", "pcsisr810" ,
                                       "pcsisr811", "pcsisr812", "pcsisr813", "pcsisr814", "pcsisr815",
                                       "pcsisr816", "pcsisr817"),
                           parameterization = "delta", ID.fac = "std.lv",
                           ID.cat = "Wu.Estabrook.2016", group = "tbi",
                           group.equal = "configural")

summary(baseline)

# constraints
cat(as.character(baseline))

# as.character to submit to lavaan
model.baseline <- as.character(baseline)

# Fitting baseline model in lavaan via cfa function
fit.baseline <- cfa(model.baseline, data = tbi.pcsisr8, group = "tbi",
                     ordered = c("pcsisr801", "pcsisr802", "pcsisr803", "pcsisr804", "pcsisr805" , 
                                 "pcsisr806", "pcsisr807", "pcsisr808", "pcsisr809", "pcsisr810" ,
                                 "pcsisr811", "pcsisr812", "pcsisr813", "pcsisr814", "pcsisr815",
                                 "pcsisr816", "pcsisr817"), std.lv = TRUE) # covariance matrix of latent
                                                            # variables is not positive definite

lavInspect(fit.baseline, "cov.lv")

# results
summary(fit.baseline)

# adding results to matrix
all.results.pcsisr8[1,]<-round(data.matrix(fitmeasures(fit.baseline,
                                                       fit.measures = c("chisq.scaled", "df.scaled", 
                                                                        "pvalue.scaled", "rmsea.scaled",
                                                                        "rmsea.ci.lower.scaled",
                                                                        "rmsea.ci.upper.scaled",
                                                                        "cfi.scaled","tli.scaled",
                                                                        "srmr"))),
                       digits=3)

fitmeasures(fit.baseline, "chisq.scaled")/fitmeasures(fit.baseline, "df.scaled")
```

## Model with thresholds invariance

```{r}
# thresholds model
prop4c <- measEq.syntax(configural.model = eight.model,
                        data = tbi.pcsisr8,
                        ordered = c("pcsisr801", "pcsisr802", "pcsisr803", "pcsisr804", "pcsisr805" , 
                                    "pcsisr806", "pcsisr807", "pcsisr808", "pcsisr809", "pcsisr810" ,
                                    "pcsisr811", "pcsisr812", "pcsisr813", "pcsisr814", "pcsisr815",
                                    "pcsisr816", "pcsisr817"),
                        parameterization = "delta", ID.fac = "std.lv",
                        ID.cat = "Wu.Estabrook.2016", group = "tbi",
                        group.equal = c("thresholds"))

model.prop4c <- as.character(prop4c)

# fitting into lavaan
fit.prop4c <- cfa(model.prop4c, data = tbi.pcsisr8, group = "tbi",
                  ordered = c("pcsisr801", "pcsisr802", "pcsisr803", "pcsisr804", "pcsisr805" , 
                              "pcsisr806", "pcsisr807", "pcsisr808", "pcsisr809", "pcsisr810" ,
                              "pcsisr811", "pcsisr812", "pcsisr813", "pcsisr814", "pcsisr815",
                              "pcsisr816", "pcsisr817"), std.lv = TRUE) # covariance matrix of latent
                                                            # variables is not positive definite

# results
summary(fit.prop4c)

# adding results to matrix
all.results.pcsisr8[2,]<-round(data.matrix(fitmeasures(fit.prop4c,
                                                       fit.measures = c("chisq.scaled", "df.scaled", 
                                                                        "pvalue.scaled", "rmsea.scaled",
                                                                        "rmsea.ci.lower.scaled",
                                                                        "rmsea.ci.upper.scaled",
                                                                        "cfi.scaled","tli.scaled",
                                                                        "srmr"))),
                       digits=3)

fitmeasures(fit.prop4c, "chisq.scaled")/fitmeasures(fit.prop4c, "df.scaled")

# comparing the models
lavTestLRT(fit.baseline,fit.prop4c) # same measures
```

## Model with thresholds and loading invariance

```{r}
# thresholds and loading model
prop7c <- measEq.syntax(configural.model = eight.model,
                        data = tbi.pcsisr8,
                        ordered = c("pcsisr801", "pcsisr802", "pcsisr803", "pcsisr804", "pcsisr805" , 
                                    "pcsisr806", "pcsisr807", "pcsisr808", "pcsisr809", "pcsisr810" ,
                                    "pcsisr811", "pcsisr812", "pcsisr813", "pcsisr814", "pcsisr815",
                                    "pcsisr816", "pcsisr817"),
                        parameterization = "delta", ID.fac = "std.lv",
                        ID.cat = "Wu.Estabrook.2016", group = "tbi",
                        group.equal = c("thresholds", "loadings"))

model.prop7c <- as.character(prop7c)

# fitting into lavaan
fit.prop7c <- cfa(model.prop7c, data = tbi.pcsisr8, group = "tbi",
                  ordered = c("pcsisr801", "pcsisr802", "pcsisr803", "pcsisr804", "pcsisr805" , 
                              "pcsisr806", "pcsisr807", "pcsisr808", "pcsisr809", "pcsisr810" ,
                              "pcsisr811", "pcsisr812", "pcsisr813", "pcsisr814", "pcsisr815",
                              "pcsisr816", "pcsisr817"), std.lv = TRUE) # covariance matrix of latent
                                                            # variables is not positive definite

# results
summary(fit.prop7c)

# adding results to matrix
all.results.pcsisr8[3,]<-round(data.matrix(fitmeasures(fit.prop7c,
                                                       fit.measures = c("chisq.scaled", "df.scaled", 
                                                                        "pvalue.scaled", "rmsea.scaled",
                                                                        "rmsea.ci.lower.scaled",
                                                                        "rmsea.ci.upper.scaled",
                                                                        "cfi.scaled","tli.scaled",
                                                                        "srmr"))),
                       digits=3)

fitmeasures(fit.prop7c, "chisq.scaled")/fitmeasures(fit.prop7c, "df.scaled")

# comparing the models
lavTestLRT(fit.prop4c, fit.prop7c) # non-significant, prop4c
```

